True versus apparent shapes of bow shocks

### 2017-12-05 papers/Paper1/sec-conclusions.tex
Add a new appendix on the circle fits

This paper is the first of a series that will apply our shape analysis
to a wide variety of models and observations of stellar bow shocks.
In a second paper, % \citep{Henney:2018a}
we consider the alternative model of dusty radiation-driven bow wave,
instead of a hydrodynamic bow shock, and also calculate the signature
in the planitude--alatude plane of oscillations in the bow shape, which
may be due to instabilities or a time-varying source.  In a third
paper, % \citep{Henney:2018b},
we apply our techniques to observational datasets for three different
classes of stellar bow shocks: OB stars, cool giants/supergiants, and
young stars in the extended Orion Nebula.  In a fourth paper,
% \citep{Tarango-Yong:2018b},
we analyze the proplyd bow shocks in the core of the Orion Nebula.

>>>>

This paper is the first of a series that will apply our shape analysis
to a wide variety of models and observations of stellar bow shocks.
In a second paper, % \citep{Henney:2018a}
we consider the alternative model of dusty radiation-driven bow wave
\citep{Ochsendorf:2014a}, instead of a hydrodynamic bow shock, and
also calculate the signature in the planitude--alatude plane of
oscillations in the bow shape, which may be due to instabilities or a
time-varying source.  In a third paper, % \citep{Henney:2018b},
we apply our techniques to observational datasets for three different
classes of stellar bow shocks: OB stars \citep{Kobulnicky:2016a}, cool
giants/supergiants \citep{Cox:2012a}, and young stars in the extended
Orion Nebula \citep{Henney:2013a}.  In a fourth paper,
% \citep{Tarango-Yong:2018b},
we analyze the proplyd bow shocks in the core of the Orion Nebula
\citep{Garcia-Arredondo:2001a}.

### 2017-12-05 papers/Paper1/sec-intro.tex
Add a new appendix on the circle fits

A fourth parameter is the asymptotic opening angle of the far wings,
\(\theta_\infty\), which is useful in the case that the wings are asymptotically
conical.  However, in many bow shocks the wings tend towards the
asymptotic angle only slowly, making \(\theta_\infty\) difficult to measure,
especially since the emission from the far wings is often weak at
best.  In contrast, the three radii, \(R_0\), \(R_{90}\), and
\(R_{\C}\). are straightforward to determine from observations.  One
simple method to estimate the radius of curvature is to make use of
the Taylor expansion\footnote{%
  This method assumes both that \(R(\theta)\) is even (true for a
  cylindrically symmetric bow) and that the orientation of the axis is
  already known.  Generalization to cases where these assumptions do
  not hold is discussed in \citet{Henney:2018b}.} %
of \(R(\theta)\) about the apex (with \(\theta\) in
radians):
\begin{equation}
  \label{eq:taylor-R-theta}
  R(\theta) = R_0 + \frac12 R_{\theta\theta,0} \,\theta^2 + \mathcal{O}(\theta^4) \ ,
\end{equation}
so that fitting a polynomial in \(\theta^2\) to \(R(\theta)\) for
\(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_{\theta\theta,0}\) from the first two
coefficients, and hence \(R_{\C}\) from
equation~\eqref{eq:radius-curvature}.  Experience has shown that
\(\Delta\theta = 30^\circ\) and three terms in the polynomial are good choices,
where the third term is used only as a monitor (if the co-efficient of
\(\theta^4\) is not small compared with \(R_0\), then it may indicate a
problem with the fit).

>>>>

A fourth parameter is the asymptotic opening angle of the far wings,
\(\theta_\infty\), which is useful in the case that the wings are asymptotically
conical.  However, in many bow shocks the wings tend towards the
asymptotic angle only slowly, making \(\theta_\infty\) difficult to measure,
especially since the emission from the far wings is often weak at
best.  In contrast, the three radii, \(R_0\), \(R_{90}\), and
\(R_{\C}\). are straightforward to determine from observations.  One
simple method to estimate the radius of curvature is to make use of
the Taylor expansion\footnote{%
  This method assumes both that \(R(\theta)\) is even (true for a
  cylindrically symmetric bow) and that the orientation of the axis is
  already known.  Generalization to cases where these assumptions do
  not hold is discussed in Appendix~\ref{app:rcurv-empirical}.} %
of \(R(\theta)\) about the apex (with \(\theta\) in radians):
\begin{equation}
  \label{eq:taylor-R-theta}
  R(\theta) = R_0 + \frac12 R_{\theta\theta,0} \,\theta^2 + \mathcal{O}(\theta^4) \ ,
\end{equation}
so that fitting a polynomial in \(\theta^2\) to \(R(\theta)\) for
\(|\theta| < \Delta\theta \) yields \(R_0\) and \(R_{\theta\theta,0}\) from the first two
coefficients, and hence \(R_{\C}\) from
equation~\eqref{eq:radius-curvature}.  Experience has shown that
\(\Delta\theta = 30^\circ\) and three terms in the polynomial are good choices,
where the third term is used only as a monitor (if the co-efficient of
\(\theta^4\) is not small compared with \(R_0\), then it may indicate a
problem with the fit).
